Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-09-19 Paper.tex

The block in Ethereum is the collection of relevant pieces of information (known as the block \textit{header}), $H$, together with information corresponding to the comprised transactions, $\mathbf{T}$, and a set of other block headers $\mathbf{U}$ that are known to have a parent equal to the present block's parent's parent (such blocks are known as \textit{ommers}\footnote{\textit{ommer} is the most prevalent (not saying much) gender-neutral term to mean ``sibling of parent''; see \url{http://nonbinary.org/wiki/Gender_neutral_language\#Family_Terms}}). The block header contains several pieces of information:

@@

\begin{align}
\quad g' &\equiv \begin{cases}
0 & \text{if} \quad F \\
g^{**} - c & \text{otherwise} \\
\end{cases} \\
\quad \boldsymbol{\sigma}' &\equiv  \begin{cases}
\boldsymbol{\sigma} & \text{if} \quad F \\
\boldsymbol{\sigma}^{**} \quad \text{except:} & \\
\quad\boldsymbol{\sigma}'[a]_c = \texttt{\small KEC}(\mathbf{o}) & \text{otherwise}
\end{cases} \\
\nonumber \text{where} \\
F &\equiv \big(\boldsymbol{\sigma}^{**} = \varnothing \ \vee\  g^{**} < c \ \vee\  |\mathbf{o}| > 24576\big
\end{align}

The exception in the determination of $\boldsymbol{\sigma}'$ dictates that $\mathbf{o}$, the resultant byte sequence from the execution of the initialisation code, specifies the final body code for the newly-created account. Note that the 24576 byte limit for $\mathbf{o}$ exists because a contract creation call can trigger O(n) cost in terms of reading the code from disk, preprocessing the code for VM execution, and also adding O(n) data to the Merkle proof for the block's proof-of-validity. With higher gas limits that can be caused by dynamic gas limit rules, this is a greater concern, and is especially inconvenient with light clients verifying proofs of validity or invalidity.

Note that the intention is that the result is either a successfully created new contract with its endowment, or no new contract with no transfer of value.

@@

\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \begin{cases}
\boldsymbol{\sigma} & \text{if} \quad \boldsymbol{\sigma}^{**} = \varnothing \\
\boldsymbol{\sigma}^{**} & \text{otherwise}
\end{cases} \\
g' & \equiv & \begin{cases}
0 & \text{if} \quad \boldsymbol{\sigma}^{**} = \varnothing \\
g^{**} & \text{otherwise}
\end{cases} \\
\qquad (\boldsymbol{\sigma}^{**}, g^{**}, A, \mathbf{o}) & \equiv & \begin{cases}
\Xi_{\mathtt{ECREC}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 1 \\
\Xi_{\mathtt{SHA256}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 2 \\
\Xi_{\mathtt{RIP160}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 3 \\
\Xi_{\mathtt{ID}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 4 \\
\Xi(\boldsymbol{\sigma}_1, g, I) & \text{otherwise} \end{cases} \\
I_a & \equiv & r \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & \tilde{v} \\
I_e & \equiv & e \\
\text{Let} \; \mathtt{\tiny KEC}(I_\mathbf{b}) & = & \boldsymbol{\sigma}[c]_c
\end{eqnarray}

@@

>>>>

The block in Ethereum is the collection of relevant pieces of information (known as the block \textit{header}), $H$, together with information corresponding to the comprised transactions, $\mathbf{T}$, and a set of other block headers $\mathbf{U}$ that are known to have a parent equal to the present block's parent's parent (such blocks are known as \textit{ommers}\footnote{\textit{ommer} is the most prevalent (not saying much) gender-neutral term to mean ``sibling of parent''; see \url{http://nonbinary.org/wiki/Gender_neutral_language#Family_Terms}}). The block header contains several pieces of information:

@@

\begin{align}
\quad g' &\equiv \begin{cases}
0 & \text{if} \quad \boldsymbol{\sigma}^{**} = \varnothing \\
g^{**} & \text{if} \quad g^{**}<c \wedge H_i<\firsthomesteadblock \\
g^{**} - c & \text{otherwise} \\
\end{cases} \\
\quad \boldsymbol{\sigma}' &\equiv  \begin{cases}
\boldsymbol{\sigma} & \text{if} \quad \boldsymbol{\sigma}^{**} = \varnothing \\
\boldsymbol{\sigma}^{**} & \text{if} \quad g^{**}<c \wedge H_i<\firsthomesteadblock \\
\boldsymbol{\sigma}^{**} \quad \text{except:} & \\
\quad\boldsymbol{\sigma}'[a]_c = \texttt{\small KEC}(\mathbf{o}) & \text{otherwise}
\end{cases}
\end{align}

The exception in the determination of $\boldsymbol{\sigma}'$ dictates that $\mathbf{o}$, the resultant byte sequence from the execution of the initialisation code, specifies the final body code for the newly-created account.

Note that the intention from block \firsthomesteadblock\ onwards ({\it Homestead}) is that the result is either a successfully created new contract with its endowment, or no new contract with no transfer of value. Before {\it Homestead}, if there is not enough gas to pay $c$, an account at the new contract's address is created, along with all the initialisation side-effects, and the value is transferred, but no contract code is deployed.

@@

\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \begin{cases}
\boldsymbol{\sigma} & \text{if} \quad \boldsymbol{\sigma}^{**} = \varnothing \\
\boldsymbol{\sigma}^{**} & \text{otherwise}
\end{cases} \\
(\boldsymbol{\sigma}^{**}, g', \mathbf{s}, \mathbf{o}) & \equiv & \begin{cases}
\Xi_{\mathtt{ECREC}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 1 \\
\Xi_{\mathtt{SHA256}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 2 \\
\Xi_{\mathtt{RIP160}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 3 \\
\Xi_{\mathtt{ID}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 4 \\
\Xi_{\mathtt{BN\_ADD}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 5 \\
\Xi_{\mathtt{BN\_MUL}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 6 \\
\Xi_{\mathtt{SNARKV}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 7 \\
\Xi(\boldsymbol{\sigma}_1, g, I) & \text{otherwise} \end{cases} \\
I_a & \equiv & r \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & \tilde{v} \\
I_e & \equiv & e \\
\text{Let} \; \mathtt{\tiny KEC}(I_\mathbf{b}) & = & \boldsymbol{\sigma}[c]_c
\end{eqnarray}

@@

\subsection{zkSNARK Related Precompiled Contracts}

We choose two numbers, both of which are prime.
\begin{eqnarray}
p &\equiv& 21888242871839275222246405745257275088696311157297823662689037894645226208583 \\
q &\equiv& 21888242871839275222246405745257275088548364400416034343698204186575808495617
\end{eqnarray}
Since $p$ is a prime number, $\{0, 1, \ldots, p - 1\}$ forms a field with addition and multiplication modulo $p$. We call this field $F_p$.

We define a set~$C_1$ with
\begin{equation}
C_1\equiv\{(X,Y)\in F_p\times F_p\mid Y^2=X^3+3\}\cup\{(0,0)\}
\end{equation}
We define a binary operation $+$ on $C_1$ with
\begin{eqnarray}\label{eq:ec-addition}
(X_1, Y_1) + (X_2, Y_2)&\equiv&\begin{cases}
(X,Y)&\text{if}\ X_1\neq X_2\\
(0,0)&\text{otherwise}
\end{cases}\\
X&\equiv&\lambda^2-X_1-X_2\\
Y&\equiv&\lambda(X_1-X)-Y_1\\
\lambda&\equiv&\frac{Y_2-Y_1}{X_2-X_1}
\end{eqnarray}

$(C_1,+)$ is known to form a group. We define the scalar multiplication $\cdot$ with
\begin{equation}\label{eq:ec-scalar-multiplication}
n\cdot P\equiv(0,0)+\underbrace{P+\cdots+P}_{n}
\end{equation}
for a natural number $n$ and a point $P$ in $C_1$.

We define $P_1$ to be a point $(1,2)$ on $C_1$. Let $G_1$ be the subgroup of $(C_1,+)$ generated by $P_1$. $G_1$ is known to be a cyclic group of order $q$. For a point $P$ in $G_1$, we define $\log_{P_1}(P)$ to be the smallest natural number $n$ satisfying $n\cdot P_1=P$. $\log_{P_1}(P)$ is at most $q-1$.

Let $F_{p^2}$ be a field $F_p[i]/(i+1)$. We define a set $C_2$ with
\begin{equation}
C_2\equiv\{(X,Y)\in F_{p^2}\times F_{p^2}\mid Y^2=X^3+3\}\cup\{(0,0)\}
\end{equation}
We define a binary operation $+$ and a scalar multiplication $\cdot$ with the same equations (\ref{eq:ec-addition}) and (\ref{eq:ec-scalar-multiplication}). $(C_2,+)$ is also known to be a group. We define $P_2$ in $C_2$ with
\begin{eqnarray}
P_2&\equiv&
(11559732032986387107991004021392285783925812861821192530917403151452391805634 \times i\\\nonumber &&+ 10857046999023057135944570762232829481370756359578518086990519993285655852781,\\\nonumber && 4082367875863433681332203403145435568316851327593401208105741076214120093531 \times i\\\nonumber &&+ 8495653923123431417604973247489272438418190587263600148770280649306958101930)
\end{eqnarray}
We define $G_2$ to be the subgroup of $(C_2,+)$ generated by $P_2$. $G_2$ is known to be a cyclic group of order $q$. For a point $P$ in $G_2$, we define $\log_{P_2}(P)$ be the smallest natural number $n$ satisfying $n\cdot P_2=P$. With this definition, $\log_{P_2}(P)$ is at most $q-1$.

A 32 byte number $\mathbf{x}\in\mathbf{P}_{256}$ might and might not represent an element of $F_p$.
\begin{equation}
\delta_p(\mathbf x)\equiv\begin{cases}
\mathbf x&\text{if}\ \mathbf x<p\\
\varnothing&\text{otherwise}
\end{cases}
\end{equation}

A 64 byte data $\mathbf x\in\mathbf B_{512}$ might and might not represent an element of $G_1$.
\begin{eqnarray}
\delta_1(\mathbf x)&\equiv&\begin{cases}
g_1&\text{if}\ g_1\in G_1\\
\varnothing&\text{otherwise}
\end{cases}\\
g_1&\equiv&\begin{cases}
(x,y)&\text{if}\ x\neq\varnothing\wedge y\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x&\equiv&\delta_p(\mathbf x[0..31])\\
y&\equiv&\delta_p(\mathbf x[32..63])
\end{eqnarray}

A 128 byte data $\mathbf x\in\mathbf B_{1024}$ might and might not represent an element of $G_2$.
\begin{eqnarray}
\delta_2(\mathbf x)&\equiv&\begin{cases}
g_2&\text{if}\ g_2\in G_2\\
\varnothing&\text{otherwise}
\end{cases}\\
g_2&\equiv&\begin{cases}
((x_0i+y_0),(x_1i+y_1))&\text{if}\ x_0\neq\varnothing\wedge y_0\neq\varnothing\wedge x_1\neq\varnothing\wedge y_1\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x_0&\equiv&\delta_p(\mathbf x[0..31])\\
y_0&\equiv&\delta_p(\mathbf x[32..63])\\
x_1&\equiv&\delta_p(\mathbf x[64..95])\\
y_1&\equiv&\delta_p(\mathbf x[96..127])
\end{eqnarray}

We define a precompiled contract for zkSNARK verification.
\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ F\\
F&\equiv&(|I_\mathbf{d}|\bmod 192\neq 0\vee(\exists j.\ a_j=\varnothing\vee b_j=\varnothing))\\
k &=& \dfrac{|I_\mathbf{d}|}{192} \\
g_r&=& 60000k + 40000 \\
\mathbf o[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_k)\times\log_{P_2}(b_k)\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf d}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf d}[64..191])\\\nonumber
\vdots\\
a_k&\equiv&\delta_1(I_{\mathbf d}[(|I_{\mathbf d}|-192)..(|I_{\mathbf d}|-129)])\\
b_k&\equiv&\delta_2(I_{\mathbf d}[(|I_{\mathbf d}|-128)..(|I_{\mathbf d}|-1)])
\end{eqnarray}

We define a precompiled contract for addition on $G_1$.
\begin{eqnarray}
\Xi_{\mathtt{BN\_ADD}}&\equiv&\Xi_{\mathtt{BN\_PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_ADD}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ x=\varnothing\vee y=\varnothing\\
g_r &=& 500\\
\mathbf o&\equiv&\delta_1^{-1}(x+y)\quad\text{where $+$ is the group operation in $G_1$}\\
x&\equiv&\delta_1(\bar I_{\mathbf d}[0..63])\\
y&\equiv&\delta_1(\bar I_{\mathbf d}[64..127])\\
\label{eq:complemented_input}\bar I_{\mathbf d}[x]&\equiv&\begin{cases}
I_{\mathbf d}[x]&\text{if}\ x < |I_{\mathbf d}|\\
0&\text{otherwise}
\end{cases}
\end{eqnarray}

We define a precompiled contract for scalar multiplication on $G_1$, where $\bar I_{\mathbf d}$ is defined in (\ref{eq:complemented_input}).
\begin{eqnarray}
\Xi_{\mathtt{BN\_MUL}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_MUL}}(\boldsymbol\sigma,g,I)&=&(\varnothing,0,A^0,())\quad\text{if}\ x=\varnothing\\
g_r &=& 40000\\
\mathbf o&\equiv&\delta_1^{-1}(n\cdot x)\quad\text{where $\cdot$ is the scalar multiplication in $G_1$}\\
n&\equiv&\bar I_{\mathbf d}[0..31]\\
x&\equiv&\delta_1(\bar I_{\mathbf d}[32..95])
\end{eqnarray}
